\textbf{The statistical analysis of non-linear longitudinal data in biomedical research using generalized additive models}

### 2021-06-02 Manuscripts/Manuscript by chapters -v2/02-Challenges.Rmd
Manuscript with final changes from JT added. Need to tweak the shades in the pairwise comparison plots

## What does an rm-ANOVA fit looks like? A visual representation using simulated data{#simulation}

@@

Briefly, two cases for the mean responses for each group are considered: in the first case, the mean response in each group is a linear function with different intercepts and slopes; a negative slope is used for Group 1 and a positive slope is used for Group 2 (Figure \@ref(fig:l-q-response), A). In the second case, a second-degree polynomial (quadratic) function is used for the mean response per group: the quadratic function is concave down for Group 1 and it is concave up for Group 2 (Figure \@ref(fig:l-q-response), C). In both the linear and quadratic simulated data, the groups start with the same mean value at the first time point. This is intentional in order to simulate the expected temporal evolution of some physiological quantity, which is typical in biomedical experiments.

Specifically, the rationale for the chosen linear and quadratic functions is the likelihood that a measured response in two treatment groups is similar in the initial phase of the study, but as therapy progresses a divergence in the trend of the response indicates a treatment effect. In other words, Group 1 can be thought as a "Control" group and Group 2 as a "Treatment" group. From the mean response per group (linear or quadratic), the variability or "error" of individual responses  within each group is simulated using a covariance matrix with compound symmetry (constant variance across time). Thus, the response per subject in both the linear and quadratic simulation corresponds to the mean response per group plus the error (Figure \@ref(fig:l-q-response) B,D).

>>>>

## What do an rm-ANOVA and LMEM fit look like? A visual representation using simulated data{#simulation}

@@

Briefly, two cases for the mean responses for each group are considered: in the first case, the mean response in each group is a linear function over time with different intercepts and slopes; a negative slope is used for Group 1 and a positive slope is used for Group 2 (Figure \@ref(fig:l-q-response), A). In the second case, a second-degree polynomial (quadratic) function is used for the mean response per group: the quadratic function is concave down for Group 1 and it is concave up for Group 2 (Figure \@ref(fig:l-q-response), C). In both the linear and quadratic simulated data, the groups start with the same mean value at the first time point. This is intentional in order to simulate the expected temporal evolution of some physiological quantity, which is typical in biomedical experiments.

Specifically, the rationale for the chosen linear and quadratic functions is the expectation that a measured response in two treatment groups is similar in the initial phase of the study, but as therapy progresses a divergence in the trend of the response indicates a treatment effect. In other words, Group 1 can be thought as a "Control" group and Group 2 as a "Treatment" group. From the mean response per group (linear or quadratic), the variability or "error" of individual responses  within each group is simulated using a covariance matrix with compound symmetry (constant variance across time). Thus, the response per subject in both the linear and quadratic simulation corresponds to the mean response per group plus the error (Figure \@ref(fig:l-q-response) B,D).

### 2021-06-02 Manuscripts/Manuscript by chapters -v2/03-GAM Theory.Rmd
Manuscript with final changes from JT added. Need to tweak the shades in the pairwise comparison plots

In contrast to the linear functions used to model the relationship between the covariates and the response in rm-ANOVA or LMEM, GAMs use more flexible _smooth functions_. This approach is advantageous as it does not restrict the model to a linear relationship, although a GAM will estimate a linear relationship if the data is consistent with a linear response. One possible set of functions for $f(x_t\mid \beta_j)$ that allow for non-linear responses are polynomials, but a major limitation is that polynomials create a "global" fit as they assume that the same relationship exists everywhere, which can cause problems with inference [@beck1998]. In particular, polynomial fits are known to show boundary effects because as $t$ goes to $\pm \infty$, $f(x_t \mid \beta_j)$ goes to $\pm \infty$ which is almost always unrealistic, and causes bias at the endpoints of the time period.

The smooth functional relationship between the covariates and the response in GAMs is specified   using a semi-parametric relationship that can be fit within the GLM framework, by using _basis function_ expansions of the covariates and by estimating random coefficients associated with these basis functions. A _basis_ is a set of functions that spans the mathematical space where the smooths that approximate $f(x_t \mid \beta_j)$ exist [@simpson2018]. For the linear model in Equation \@ref(eq:linear-model), the basis coefficients are $\beta_1$, $\beta_2$ and $\beta_3$ and the basis vectors are $time_t$, $treatment_j$ and $time_t \times treatment_j$. The basis function then, is the combination of basis coefficients and basis vectors that map the possible relationship between the covariates and the response [@hefley2017], which in the case of Equation \@ref(eq:linear-model) is restricted to a linear family of functions.  In the case of Equation \@ref(eq:GAM), the basis function is $f(x_t\mid \beta_j)$, which means that the model allows for non-linear relationships among the covariates.

Commonly used _basis functions_ are splines (cubic, thin plate regression among others). A cubic spline is a smooth curve constructed from cubic polynomials joined together in a manner that enforces smoothness, and thin plate regression splines are an optimized version that work well with noisy data [@wood2017;@simpson2018]. Splines have a long history in solving semi-parametric statistical problems and are often a default choice to fit GAMs as they are a simple, flexible and powerful option to obtain smoothness [@wegman1983]. Therefore, this data-driven flexibility in GAMs overcomes the limitation that occurs in LMEMs and rm-ANOVA when the data is non linear.

To further clarify the concept of basis functions and smooth functions, consider the simulated response for Group 1 in Figure (\@ref(fig:l-q-response), C). The simplest GAM model that can be used to estimate such response is that of a single smooth term for the time effect; i.e., a model that fits a smooth to the trend of the group through time. The timeline can be divided in equally spaced _knots_, each knot being a region where a different basis function will be used. Because there are six timepoints for this group, five knots can be used. The model with five knots to construct the smooth term means that it will have four basis functions (plus one that corresponds to the intercept). The choice of basis functions is already optimized in the package _mgcv_ depending on the number of knots. In Panel A of Figure \@ref(fig:basis-plot), the four basis functions (and the intercept) are shown. Each of the basis functions is composed of six different points (because there are six points on the timeline). To control the "wigliness" of the fit, each of the basis functions of Panel A is weighted by multiplying it by a coefficient according to the matrix of Panel B. The parameter estimates are penalized where the penalty reduces the "wigliness" of the smooth fit to prevent overfitting: A weak penalty estimate will result in wiggly functions whereas a strong penalty estimate provides evidence that a linear response is appropriate.

@@

In other words, the six points of each basis are multiplied by the corresponding coefficient in panel B, thereby increasing or decreasing the original basis functions of Panel A. In Figure \@ref(fig:basis-plot), Panel C shows the resulting penalized basis functions. Note that the penalization for basis 1 has resulted in a decrease of its overall value (because the coefficient for that basis function is negative and less than 1); on the other hand, basis 3 has roughly doubled its value. Finally, the penalized basis functions are added at each timepoint to produce the smooth term. The resulting smooth term for the effect of _time_ is shown in Panel D (orange line) along the simulated values per group, which appear as points.

(ref:basis-plot-caption) Basis functions for a single smoother for time with five knots. A: Basis functions for a single smoother for time for the simulated data of Group 1 from Figure 2, the intercept basis is not shown. B: Matrix for basis function penalization. Each basis function is multiplied by a coefficient which can be positive or negative. The coefficient determines the overall effect of each basis in the final smoother. C: Weighted basis functions. Each of the four basis functions of panel A has been weighted by the corresponding coefficient shown in Panel B, note the corresponding increase (or decrease) of each basis. D: Smoother for time and original data points. The smoother (line) is the result of the sum of each penalized basis function at each time point, with simulated values for the group shown as points.

>>>>

In contrast to the linear functions used to model the relationship between the covariates and the response in rm-ANOVA or LMEM, GAMs use more flexible _smooth functions_. This approach is advantageous as it does not restrict the model to a linear relationship, although a GAM will estimate a linear relationship if the data is consistent with a linear response. One possible set of functions for $f(x_t\mid \beta_j)$ that allow for non-linear responses are polynomials, but a major limitation is that polynomials create a "global" fit as they assume that the same relationship exists everywhere, which can cause problems with inference [@beck1998]. In particular, polynomial fits are known to show boundary effects because as $t$ goes to $\pm \infty$, $f(x_t \mid \beta_j)$ goes to $\pm \infty$ which is almost always unrealistic and causes bias at the endpoints of the time period.

The smooth functional relationship between the covariates and the response in GAMs is specified   using a semi-parametric relationship that can be fit within the GLM framework, by using _basis function_ expansions of the covariates and by estimating random coefficients associated with these basis functions. A _basis_ is a set of functions that spans the mathematical space where the smooths that approximate $f(x_t\mid \beta_j)$ exist [@simpson2018]. For the linear model in Equation \@ref(eq:linear-model), the basis coefficients are $\beta_1$, $\beta_2$ and $\beta_3$ and the basis vectors are $time_t$, $treatment_j$ and $time_t \times treatment_j$. The basis function then, is the combination of basis coefficients and basis vectors that map the possible relationship between the covariates and the response [@hefley2017], which in the case of Equation \@ref(eq:linear-model) is restricted to a linear family of functions.  In the case of Equation \@ref(eq:GAM), the basis functions are $f(x_t\mid \beta_j)$, which means that the model allows for non-linear relationships among the covariates.

Splines (cubic, thin plate, etc.) are commonly used _basis functions_; a cubic spline is a smooth curve constructed from cubic polynomials joined together in a manner that enforces smoothness, and thin plate regression splines are an optimized version that work well with noisy data [@wood2017;@simpson2018]. Splines have a long history in solving semi-parametric statistical problems and are often a default choice to fit GAMs as they are a simple, flexible and powerful option to obtain smoothness [@wegman1983]. Therefore, this data-driven flexibility in GAMs overcomes the limitation that occurs in LMEMs and rm-ANOVA when the data is non linear.

To further clarify the concept of basis functions and smooth functions, consider the simulated response for Group 1 in Figure (\@ref(fig:l-q-response), C). The simplest GAM model that can be used to estimate such response is that of a single smooth term for the time effect; i.e., a model that fits a smooth to the trend of the group through time. The timeline can be divided in equally spaced _knots_, each knot being a region where a different basis function will be used. Because there are six timepoints for this group, five knots can be used. The model with five knots to construct the smooth term means that it will have four basis functions (plus one that corresponds to the intercept). The choice of basis functions is set using default values in the package _mgcv_ depending on the number of knots. In Panel A of Figure \@ref(fig:basis-plot), the four basis functions (and the intercept) are shown. Each of the basis functions is composed of six different points (because there are six points on the timeline). To control the "wiggliness" of the fit, each of the basis functions of Panel A is weighted by multiplying it by a coefficient according to the matrix of Panel B. The parameter estimates are penalized where the penalty reduces the "wiggliness" of the smooth fit to prevent overfitting: A weak penalty estimate will result in wiggly functions whereas a strong penalty estimate provides evidence that a linear response is appropriate.

@@

In other words, the six points of each basis are multiplied by the corresponding coefficient in panel B, thereby increasing or decreasing the original basis functions of Panel A. In Figure \@ref(fig:basis-plot), Panel C shows the resulting weighted basis functions. Note that the magnitude of the weighting for basis function 1 has resulted in a decrease of its overall value (because the coefficient for that basis function is less than 1). On the other hand, basis function 3 has roughly doubled its value. Finally, the weighted basis functions are added at each timepoint to produce the smooth term. The resulting smooth term for the effect of _time_ is shown in Panel D (orange line) along the simulated values per group, which appear as points.

(ref:basis-plot-caption) Basis functions for a single smoother for time with five knots. A: Basis functions for a single smoother for time for the simulated data of Group 1 from Figure 2, the intercept basis is not shown. B: Matrix for basis function weights. Each basis function is multiplied by a coefficient which can be positive or negative. The coefficient determines the overall effect of each basis in the final smoother. C: Weighted basis functions. Each of the four basis functions of panel A has been weighted by the corresponding coefficient shown in Panel B, note the corresponding increase (or decrease) of each basis. D: Smoother for time and original data points. The smoother (line) is the result of the sum of each penalized basis function at each time point, with simulated values for the group shown as points.

### 2021-06-02 Manuscripts/Manuscript by chapters -v2/04-Longitudinal analysis with GAMs.Rmd
Manuscript with final changes from JT added. Need to tweak the shades in the pairwise comparison plots

For the data in Figure \@ref(fig:sim-smooth-plot), A the main effect of interest is how $\mbox{StO}_2$ changes over time for each treatment. To estimate this, the model needs to incorporate independent smooths for _Group_ and _Day_, respectively. The main thing to consider is that model syntax accounts for the fact that one of the variables is numeric ( _Day_ ) and the other is a factor ( _Group_ ). Because the smooths are centered at 0, the factor variable needs to be specified as a parametric term in order to identify any differences between the groups. Using $\textsf{R}$ and the package `mgcv` the model syntax is:

`m1<-gam(StO2_sim~Group+s(Day,by=Group,k=5), method='REML',data=dat_sim)`

This syntax specifies that `m1` will store the model, and that the change in the simulated oxygen saturation (`StO2_sim`) is modeled using independent smooths for  _Group_ and _Day_ (the parenthesis preceded by _s_) using 5 knots. The smooth is constructed by default using thin plate regression splines. Other splines can be used if desired, including gaussian process smooths [@simpson2018]. The parametric term _Group_ is added to quantify differences in the effect of treatment between groups, and the `method` chosen to select the smoothing parameters is the restricted maximum likelihood (REML) [@wood2017]. When the smooths are plotted over the raw data, it is clear that the model has been able to capture the trend of the change of $\mbox{StO}_2$ for each group across time (Figure \@ref(fig:sim-smooth-plot),B). Model diagnostics can be obtained using the `gam.check` function, and the function `appraise` from the package _gratia_ [@gratia]. A guide for model selection and diagnostics is in the Appendix, and an in-depth analysis can be found in [@wood2017] and [@harezlak2018].

One question that might arise at this point is "what is the fit that an rm-ANOVA model produces for the simulated data?". The rm-ANOVA model, which corresponds to Equation \@ref(eq:linear-model) is presented in Figure \@ref(fig:sim-smooth-plot),C. This is a typical case of model misspecification: The slopes of each group are different, which would lead to a _p-value_ indicating significance for the treatment and time effects, but the model is not capturing the changes that occur at days 2 and between days 5 and 7, whereas the GAM model is able to do so (Figure \@ref(fig:sim-smooth-plot),B) .

@@

At the core of a biomedical longitudinal study lies the question of a significant difference between the effect of two or more treatments in different groups. Whereas in rm-ANOVA a _post-hoc_ analysis is required to answer such question by calculating some _p-values_ after multiple comparisons, GAMs can use a different approach to estimate significance. In essence, the idea behind the estimation of significance in GAMs across different treatment groups is that if the _difference_ between the confidence intervals of the fitted smooths for such groups is  non-zero, then a significant difference exists at that time point(s). The absence of a _p-value_ in this case might seem odd, but the confidence interval comparison can be conceptualized in the following manner: Different trends in each group are an indication of an effect by the treatment. This is what happens for the simulated data in Figure \@ref(fig:sim-smooth-plot), A where the chemotherapy causes $\mbox{StO}_2$ to increase over time.

@@

In a sense, the pairwise smooth comparison is more informative than a _post-hoc_ _p-value_. For biomedical studies, it is able to provide an estimate of _when_ a biological process becomes significant. This is advantageous because it can help researchers gain insight on metabolic changes and other biological processes that can be worth examining, and can help refine the experimental design of future studies in order to obtain measurements at time points where a significant change is expected.

>>>>

For the data in Figure \@ref(fig:sim-smooth-plot), A the main effect of interest is how $\mbox{StO}_2$ changes over time for each treatment. To estimate this, the model incorporates independent smooths for _Group_ and _Day_, respectively. The main thing to consider is that model syntax accounts for the fact that one of the variables is numeric (*Day*) and the other is a factor (*Group*). Because the smooths are centered at 0, the factor variable needs to be specified as a parametric term in order to identify any differences between the groups. Using $\textsf{R}$ and the package `mgcv` the model syntax is:

`m1 <- gam(StO2_sim ~ Group + s(Day, by=Group, k=5), method='REML',data=dat_sim)`

This syntax specifies that `m1` will store the model, and that the change in the simulated oxygen saturation (`StO2_sim`) is modeled using independent smooths for `Group` and `Day` (the parenthesis preceded by `s`) using 5 knots. The smooth is constructed by default using thin plate regression splines, but other splines can be used if desired, including Gaussian process smooths [@simpson2018]. The parametric term `Group` is added to quantify differences in the effect of treatment between groups, and the `method` chosen to estimate the smoothing parameters is the restricted maximum likelihood (REML) [@wood2017]. When the smooths are plotted over the raw data, it is clear that the model has been able to capture the trend of the change of $\mbox{StO}_2$ for each group across time (Figure \@ref(fig:sim-smooth-plot),B). Model diagnostics can be obtained using the `gam.check` function, and the function `appraise` from the package _gratia_ [@gratia]. A guide for model selection and diagnostics is in the Appendix, and an in-depth analysis can be found in [@wood2017] and [@harezlak2018].

One question that might arise at this point is "what is the fit that an rm-ANOVA model produces for the simulated data?". The rm-ANOVA model, which corresponds to Equation \@ref(eq:linear-model) is presented in Figure \@ref(fig:sim-smooth-plot), C. This is a typical case of model misspecification: The slopes of each group are different, which would lead to a _p-value_ indicating significance for the treatment and time effects, but the model is not capturing the changes that occur at days 2 and between days 5 and 7, whereas the GAM model is able to do so (Figure \@ref(fig:sim-smooth-plot), B) .

@@

At the core of a biomedical longitudinal study lies the question of a significant difference between the effect of two or more treatments in different groups. Whereas in rm-ANOVA a _post-hoc_ analysis is required to answer such question by calculating some _p-values_ after multiple comparisons, GAMs can use a different approach to estimate significance. In essence, the idea behind the estimation of significance in GAMs across different treatment groups is that if the _difference_ between the empirical Bayesian confidence intervals of the fitted smooths for such groups is  non-zero, then a significant difference exists at that time point(s). The absence of a _p-value_ in this case might seem odd, but the empirical Bayesian confidence interval interpretation can be conceptualized in the following manner: Different trends in each group are an indication of an effect by the treatment. This is what happens for the simulated data in Figure \@ref(fig:sim-smooth-plot), A where the chemotherapy causes $\mbox{StO}_2$ to increase over time.

@@

In a sense, the pairwise smooth comparison is more informative than a _post-hoc_ _p-value_. For biomedical studies, the smooth comparison is able to provide an estimate of _when_ and by _how much_ a biological process becomes significant. This is advantageous because it can help researchers gain insight on metabolic changes and other biological processes that can be worth examining, and can help refine the experimental design of future studies in order to obtain measurements at time points where a significant change might be expected.

### 2021-06-02 Manuscripts/Manuscript by chapters -v2/05-Discussion.Rmd
Manuscript with final changes from JT added. Need to tweak the shades in the pairwise comparison plots

Biomedical longitudinal non-linear data is particularly challenging to analyze due to the likelihood of missing observations and different correlation structures in the data, which limit the use of rm-ANOVA. Although LMEMs have started to replace rm-ANOVA as the choice to analyze biomedical data, both methods yield biased estimates when they are used to fit non-linear data as we have visually demonstrated in Section \@ref(simulation). This "model misspecification" error, also is known as"" "Type III" error [@dennis2019] is particularly important because although the _p-value_ is the common measure of statistical significance, the validity of its interpretation is determined by the agreement of the data and the model. Guidelines for statistical reporting in biomedical journals exist (the SAMPL guidelines) [@lang2015] but they have not been widely adopted and in the case of longitudinal data, we consider that researchers would benefit from reporting a visual assessment of the correspondence between the model fit and the data, instead of merely relying on a $R^2$ value.

@@

We have used $\textsf{R}$ as the software of choice for this paper because not only provides a fully developed environment to fit GAMs, but also eases simulation (which is becoming increasingly used for exploratory statistical analysis and power calculations) and provides powerful and convenient methods of visualization, which are key aspects that biomedical researchers might need to consider to make their work reproducible. In this regard, reproducibility is still an issue in biomedical research [@begley2015;@weissgerber2018], but it is becoming apparent that what other disciplines have experienced in this aspect is likely to impact soon rather than later this field. Researchers need to plan on how they will make their data, code, and any other materials open and accessible as more journals and funding agencies recognize the importance and benefits of open science in biomedical research. We have made all the data and code used in this paper accessible, and we hope that this will encourage other researchers to do the same with future projects.

>>>>

Biomedical longitudinal non-linear data is particularly challenging to analyze due to the likelihood of missing observations and different correlation structures in the data, which limit the use of rm-ANOVA. Although LMEMs have started to replace rm-ANOVA as the choice to analyze biomedical data, both methods yield biased estimates when they are used to fit non-linear data as we have visually demonstrated in Section \@ref(simulation). This "model misspecification" error, also is known as a "Type III" error [@dennis2019] is particularly important because although the _p-value_ is the common measure of statistical significance, the validity of its interpretation is determined by the agreement of the data and the model. Guidelines for statistical reporting in biomedical journals exist (the SAMPL guidelines) [@lang2015] but they have not been widely adopted and in the case of longitudinal data, we consider that researchers would benefit from reporting a visual assessment of the correspondence between the model fit and the data, instead of merely relying on a $R^2$ value.

@@

We have used $\textsf{R}$ as the software of choice for this paper because not only provides a fully developed environment to fit GAMs, but also eases simulation (which is becoming increasingly used for exploratory statistical analysis and power calculations) and provides powerful and convenient methods of visualization, which are key aspects that biomedical researchers might need to consider to make their work reproducible. In this regard, reproducibility is still an issue in biomedical research [@begley2015;@weissgerber2018], but it is becoming apparent that what other disciplines have experienced in this aspect is likely to impact sooner rather than later this field. Researchers need to plan on how they will make their data, code, and any other materials open and accessible as more journals and funding agencies recognize the importance and benefits of open science in biomedical research. We have made all the data and code used in this paper accessible, and we hope that this will encourage other researchers to do the same with future projects.

### 2021-06-02 Manuscripts/Manuscript by chapters -v2/07-Appendix.Rmd
Manuscript with final changes from JT added. Need to tweak the shades in the pairwise comparison plots

(ref:basis-caption-appendix) Basis functions for a single smoother for time with five knots. A: Basis functions for a single smoother for time for the simulated data of Group 1 from Figure 2, the intercept basis is not shown. B: Penalty matrix for the basis functions. Each basis function is penalized by a coefficient which can be positive or negative. The coefficient determines the overall effect of each basis in the final smoother. C: Penalized basis functions. Each of the four basis functions of panel A has been penalized by the corresponding coefficient shown in Panel B, note the corresponding increase (or decrease) of each basis. D: Smoother for time and original data points. The smoother (line) is the result of the sum of each penalized basis function at each time point, simulated values for the group appear as points.

@@

The resulting model is`m1`, which is the model fitted in the main manuscript. By using `appraise()` and `draw` on this model (Figure  \@ref(fig:final-GAM-diag)) we see that the trend on the QQ plot has improved, the histogram of the residuals appears to be reasonably distributed, and the smooths are capturing the trend of the data within each group . From `gam.check`, the k-index is now at an acceptable value ($\approx$ 1.02), and `summary` now indicates that the model is able to capture 87% of the variance data.

@@

The output in this case is expected: model `gam1` has a lower AIC (711.46) whereas the initial two models have higher AICs (891 and 850). The AIC should not be considered as the only estimator of model goodness, instead to be used as complimentary information to the graphical diagnostics and model checks described above.

>>>>

(ref:basis-caption-appendix) Basis functions for a single smoother for time with five knots. A: Basis functions for a single smoother for time for the simulated data of Group 1 from Figure 2, the intercept basis is not shown. B: Coefficient matrix for the basis functions. Each basis function is weighted by a coefficient which can be positive or negative. The coefficient determines the overall effect of each basis in the final smoother. C: Weighted basis functions. Each of the four basis functions of panel A has been weighted by the corresponding coefficient shown in Panel B, note the corresponding increase (or decrease) of each basis. D: Smoother for time and original data points. The smoother (line) is the result of the sum of each penalized basis function at each time point, simulated values for the group appear as points.

@@

The resulting model is `m1`, which is the model fitted in the main manuscript. By using `appraise()` and `draw` on this model (Figure  \@ref(fig:final-GAM-diag)) we see that the trend on the QQ plot has improved, the histogram of the residuals appears to be reasonably distributed, and the smooths are capturing the trend of the data within each group. From `gam.check`, the k-index is now at an acceptable value ($\approx$ 1.02), and `summary` now indicates that the model is able to capture 87% of the variance data.

@@

The output in this case is expected: model `gam1` has a lower AIC (711.46) whereas the initial two models have higher AICs (891 and 850). The AIC should not be considered as the only estimator of model quality, instead to be used as complimentary information to the graphical diagnostics and model checks described above.
